\section{Software Description}

pfsense Plus software is a powerful firewall, router, and VPN solution that leverages a number of highly-regarded open-source projects. The software competes effectively with far more expensive, commercial alternatives and is used by hundreds of thousands of businesses, educational institutions, and government agencies all over the world. Leading secure-networking features and capabilities include:

\begin{itemize}
    \item Ad blocker (pfBlockerNG)
    \item Captive Portal
    \item CARP / HA
    \item DNS Server
    \item DHCP Server
    \item HTTP transparent / web / reverse proxy (Squid)
    \item IP / Country block list (pfBlocker)
    \item IDS/IPS
    \item Packet capture / inspection
    \item Port forwarding
    \item QOS / rate limiters
    \item Software load balancer (HA Proxy)
    \item Traffic monitoring
    \item Traffic logging, statistics, and graphs
    \item Traffic shaping
    \item VLAN
    \item Wake-on-LAN
    \item Website blocker (pfBlocker)
\end{itemize}

\subsection{Key features}

\subsubsection{Low total cost of ownership}

\begin{itemize}
    \item No artificial limits or add-ons are required to make your system fully functional.
    \item No additional usage or feature-based pricing. Enjoy unlimited users, unlimited firewall rules, unlimited IPsec tunnels, dual WAN, etc.
    \item Standard configuration with 16GB of RAM and 256GB Micron M.2 SSD*.
    \item Low power requirements to help save you money.
    \item This system is designed for a long deployment lifetime.
\end{itemize}

\subsubsection{Growth}

\begin{itemize}
    \item From firewall to Unified Threat Management, get all the security features you need to protect your home or business.
    \item Flexible configuration and support for multi-WAN, high availability, VPN, load balancing, reporting, and monitoring, etc.
    \item Add optional packages such as Snort or Suricata for IDS/IPS and network security monitoring, Squid for optimized content delivery, and SquidGuard for \item anti-spam/anti-phishing and URL filtering. 1 
    \item Maximum Active Connections: 16,000,000 (32,000,000 with 32 GB RAM)
\end{itemize}

\subsubsection{GUI Management}

\begin{itemize}
    \item Manage pfsense Plus software settings through our web-based GUI.
    \item No fumbling with a command-line interface or typing arcane commands.
\end{itemize}

\subsubsection{Secure Remote Access}

\begin{itemize}
    \item Connect via encrypted Virtual Private Networks (VPN) between your offices, let mobile workers connect securely, or connect to the Cloud.
    \item Use the built-in Amazon VPC Wizard to easily establish VPN connections with your Amazon EC2 cloud.
\end{itemize}

\subsubsection{Best For}

\begin{itemize}
    \item Medium to Large Sized Networks with 1U rack mount cabinets
    \item Medium to Large Sized Branch Office with heavy loads
    \item Managed Service Providers (MSP) / Managed Security Service Provider (MSSP) On-Premises Appliance
    \item Enterprise
    \item Anyone with High-Speed 10 Gigabit and/or 1 Gigabit Connections 
    \item Anyone with many VPN Connections
    \item Anyone with high-speed connections who wish to configure IDS/IPS features
\end{itemize}


